\documentclass{article}

\usepackage{amsmath}
\usepackage{csquotes}

\begin{document}

\section{Background}
Yesterday, Vlad and I discussed the problem of how much information is leaked
by different queries.
%
I raised the issue that some queries seem to leak large amounts of information
which gives an attacker a cross section of information about the entire
database structure.
%
Specifically I posed this email:

\begin{displayquote}
I've been spending some time thinking about information leakage in Blind Seer.

And more specifically, I'm having trouble understanding how allowing `and'
queries doesn’t immediately cause huge issues. Last time we discussed wanting
to discover whether or not a person makes a certain amount of money, say. It
seems to me that as soon as someone is able to ask one question about the
amount of money individuals in the database make and another about the names of
individuals in the database they certainly seemed to have gained a lot of
information with regard to their malicious question.

Or another way to put this is it seems like every query you're allowed to issue
allows you to characterize the labels the nodes in the database tree very
rapidly (basically each query tells you something about \emph{every} node in the
tree).

I guess just overall I'm trying to understand what sorts of guarantees (if any)
Blind Seer gives. Is there any literature I can refer to in order to get a
grasp on this stuff? For example, you mentioned that we know that pure `or'
queries don’t reveal information beyond the output of the query. While I
understand the argument you gave the last time we met, I was hoping there might
be something written down that might give more insight into how `and' leaks
information.
\end{displayquote}
%


\section{Notes}

Fixed database
And set of queries
Leakage property
Can the set of queries reveal property
Some database where this property is leaked?

How to take distributional reasoning and encoding it as SMT somehow?

Model Counting
How many satisfying assignments to each formula?
Formalize the policy
  What does the attacker assume
  Finite execution of a query
  Know concrete queries and concrete database
  How is attacker knowledge represented

Find way to represent the question
  Alice calls Bob
  Did Alice call Charlie?

Allowed Leakage "does it fall within allowed leakage?"
Access Control Policy "which queries are allowed?"

\end{document}
